### 2018-04-08 Manuscript/chapter4.tex
Draft to review during meeting on 20180409

\documentclass[11pt,a4paper,oldfontcommands,openany]{memoir}
\usepackage{graphicx}
\usepackage[]{color}
\usepackage{courier}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[breakable, theorems, skins]{tcolorbox}
\usepackage[]{media9}
\usepackage{lipsum}
\tcbset{enhanced}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

@@

We also compare the main effect of IAPV exposure in our dataset to that obtained in a previous study conducted by Galbraith and colleagues (\citealt{galbraith}). While our study examined honeybees from polyandrous colonies, the Galbraith study examined honeybees from single-drone colonies. As a consequence, our honeybees will have on average about 75\% genetic variance, and the honeybees from the Galbraith study will have about 25\% genetic variance (\citealt{sisters}). We should therefore expect that the Galbraith study may generate data with lower signal:to:noise ratios than our data due to the lower genetic variation between its replicates. At the same time, our honeybees will be more likely to display the health benefits gained from increased genotypic variation within colonies, including decreased parasitic load (\citealt{multParasite}), increased tolerance to environmental changes (\citealt{divHyp2}), and increasead colony performance (\citealt{geneticDiverse}, \citealt{geneticDiverse2}). Given that honeybees are naturally very polyandrous (\citealt{patriline}), our honeybees may also reflect more realistic environmental and genetic simulations. Taken together, each study provides a different point of value: Our study likely presents less artificial data while the Galbraith data likely presents less messy data. We wish to examine how the gene expression effects of IAPV innoculation compare between these two studies that used such different experimental designs. Namely, we use visualization techniques to assess the signal:to:noise ratios between these two datasets, and differential gene expression (DEG) analyses to assess any overlaps between these two datasets.

@@

@@

>>>>

\documentclass[11pt,a4paper,oldfontcommands,openany]{memoir}
\usepackage{graphicx}
\usepackage[]{color}
\usepackage{courier}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[breakable, theorems, skins]{tcolorbox}
\usepackage[]{media9}
\usepackage{lipsum}

\usepackage{lineno} %% LINE COUNTS
\linenumbers %% LINE COUNTS

\tcbset{enhanced}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

@@

We also compare the main effect of IAPV exposure in our dataset to that obtained in a previous study conducted by Galbraith and colleagues (\citealt{galbraith}). While our study examines honeybees from polyandrous colonies, the Galbraith study examined honeybees from single-drone colonies. As a consequence, our honeybees will have an average of about 75\% genetic variance, and the honeybees from the Galbraith study will have an average of about 25\% genetic variance (\citealt{sisters}). We should therefore expect that the Galbraith study may generate data with lower signal:to:noise ratios than our data due to the lower genetic variation between its replicates. At the same time, our honeybees will be more likely to display the health benefits gained from increased genotypic variance within colonies, including decreased parasitic load (\citealt{multParasite}), increased tolerance to environmental changes (\citealt{divHyp2}), and increasead colony performance (\citealt{geneticDiverse}, \citealt{geneticDiverse2}). Given that honeybees are naturally very polyandrous (\citealt{patriline}), our honeybees may also reflect more realistic environmental and genetic simulations. Taken together, each study provides a different point of value: Our study likely presents less artificial data while the Galbraith data likely presents less messy data. We wish to explore how the gene expression effects of IAPV innoculation compare between these two studies that used such different experimental designs. To achieve this objective, we use visualization techniques to assess the signal:to:noise ratio between these two datasets, and differential gene expression (DEG) analyses to determine any significantly overlapping genes of interest between these two datasets. It is our hope that this aspect of our study may shine light on how experimental designs that control genetic variability to different extents might affect the resulting gene expression data in honeybees.

@@

@@@ Which body tissue was used for RNA extraction?

@@

@@@ What percent of reads mapped?
